Brain region specific differential expression analysis (all 7 regions/one region at a time)

### 2017-05-08 code/Rmd/regionLevelDiffExpAnlz.Rmd

@@

```{r fxn}
performDifferentialExpression <- function(cov, cnt, contVar, varOfInterest, n){

  diffExp = foreach(i = 1:n, 
                    .combine = rbind,
                    .packages = c('limma','edgeR','cqn','dplyr','plyr','CovariateAnalysis')) %dopar% {

@@

### Perform differential expression (per brain region)
```{r diff.exp}
all.results = plyr::dlply(covariates, .(BrainRegion), .fun = function(cov, cnt){
  n = 5
  # Filter counts and covariates
  cnt = cnt[,cov$SampleID]

@@

  baseDiffExp <- performDifferentialExpression(cov, cnt, contVar, varOfInterest, n)

@@

  genderDiffExp <- performDifferentialExpression(cov, cnt, contVar, varOfInterest, n)

  return(rbindlist(list(baseDiffExp, genderDiffExp), use.names = T, fill = T))
}, counts)

>>>>

library(foreach)
library(doParallel)

cl = makeCluster(detectCores()-2)
registerDoParallel(cl)

@@

```{r fxn}
performDifferentialExpression <- function(cov, cnt, contVar, varOfInterest, n, gene.len, gene.gc){

  diffExp = foreach(i = 1:n, 
                    .combine = rbind,
                    .packages = c('limma','edgeR','cqn','dplyr','plyr','CovariateAnalysis','data.table'),
                    .export = c('gene.len', 'gene.gc')) %dopar% {

@@

### Perform differential expression (per brain region)
```{r diff.exp}
all.results = plyr::dlply(covariates, .(BrainRegion), .fun = function(cov, cnt, gene.len, gene.gc){
  n = 100
  # Filter counts and covariates
  cnt = cnt[,cov$SampleID]

@@

  baseDiffExp <- performDifferentialExpression(cov, cnt, contVar, varOfInterest, n, gene.len, gene.gc)

@@

  genderDiffExp <- performDifferentialExpression(cov, cnt, contVar, varOfInterest, n, gene.len, gene.gc)

  return(rbindlist(list(baseDiffExp, genderDiffExp), use.names = T, fill = T))
}, counts, gene.len, gene.gc)
